%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  THIS TEX FILE IS TO GENERATE PDF FILE FOR 
%%% 
%%%  COPYRIGHT (C) JIMMY LIN, 2013, UT AUSTIN
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt,a4paper]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  PACKAGES USED IN THIS TEX SOURCE FILE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{geometry,amsthm,amsmath,graphicx,fancyheadings}
\usepackage[colorlinks,
            linkcolor=blue,
            anchorcolor=red,
            citecolor=green
            ]{hyperref}
\usepackage{/Users/JimmyLin/workspace/latexTemplate/UTA_CS/JS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% MACROS CONTAINING THE FILE INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Some thoughts about Job Recommender System}
\author{Jimmy Lin}
\date{January 31, 2014}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% DOCUMENTATION STARTS FROM HERE 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CONTENT PAGE: TABLEOFCONTENTS, LISTOFTABLES, LIST OF FIGURES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\renewcommand{\contentsname}{Questions}
%\begin{center} 
%    \tableofcontents 
    %\listoftables 
    %\listoffigures
%\end{center}
%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% GENERAL DOCUMENTATION BEGINS 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The followings are some of my thoughts in technical aspects about job
recommender System: \\

1. As to a dataset, the first thing we need to guarantee is the 
correctness of data. From the perspective of employer, the position description may be
precise because they want to find the most suitable person. However, some
company may also wish to find overqualified person in the market, in a way of
proposing high qualification in the posting.  In addition to that, from the
standpoint of applicant, the their capabilities may be overstated out of the
purpose of finding a better job (a job with higher salary). Thus, the
authenticity of literal data would be a big problem.  \\

2. Quatitative evaluation should be important for precise recommendation. What
degree of mastery of JAVA is required for a company? What
degree of JAVA is mastered by a job applicant? The degree would essentially
influence the result of suitability evaluation. However, the difficulty exists
in the fact that such degree cannot be measured simply through looking at the
frequency of a word. \\

3. Think about what kind of data we can derive at most? 

\begin{itemize}
    \item{a set of person profiles}
    \item{a set of job posting from company}
    \item{a set of job application}
    \item{a set of job acceptance cases}
\end{itemize}

   Literally,

\begin{itemize}
    \item{Job application can only show us one applicant is interested in a position.
   Thus, this data provides us little information about the suitability
   between person and job. (suitability should be bi-directional preference.)}

   \item{Job acceptance case can provide us some information about the suitability
   in the sense that the job applicant is qualified and the company prefer
   this applicant to others. But there still exists a problem: if one company
   recruit two applicants but they have different qualification, how to
   distinguish suitability in two cases? Note that the only ground truth provided here
   is only about being accepted or not.}
\end{itemize}

4. Microscopically speaking, how can a computer perceive particular logic in
job posting? For example, one company may require a programmer to possess
master of JAVA or C++. Simple natural language processing method may perceive
it as JAVA and C++ since both of them occur one time. Nevertheless, a person
who has the either java or c++ skill would qualify.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% General Documentation ends
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
